% BEÁLLÍTÁSOK - JOBB NEM VÁLTOZTATNI

\documentclass[final]{ubb_dolgozat}
\usepackage{definitions}
\usepackage{pdfpages}
\usepackage{listings}

\newcommand{\pdf}[1]{pythonCodes/#1.pdf}
%%


% milyen nyelveken akarunk forráskódot megjeleníteni
\lstloadlanguages{C, C++}

% ezt be lehet tenni MINDEGYIK megjelenítendő kód elé.
\lstset{language=C++}


%% MELYIK ÉVBEN ADJUK LE
\submityear{%
2015
}
%% MELYIK HÓNAPBAN ADJUK LE
\submitmonthHU{%
Július
}
\submitmonthRO{%
Iulie
}
\submitmonthEN{%
July
}

\titleHU{%
Forgalmi táblák felismerése
}
\titleEN{%
Road sign recognition
}

\titleRO{%
Recunoa\c{s}terea semnelor de circula\c{t}ie
}

\author{%
Szabo Ágnes-Teréz
}

%%
\tutorHU{%
Csató Lehel\\
 {\large Babe\c{s}--Bolyai Tudományegyetem,\\
 Matematika és Informatika Kar}
}

%%
\tutorRO{%
Csató Lehel\\
 {\large Universitatea Babe\c{s}--Bolyai,\\
 Facultatea de Matematic\u{a} \c{s}i Informatic\u{a} }%
}
%%
\tutorEN{%
Csató Lehel
 {\large Babe\c{s}--Bolyai University,\\
 Faculty of Mathematics and Informatics}
}


%\includeonly{bevezet}


\begin{document}

%% ABSTRAKT
\begin{abstractEN} % ANGOL VÁLTOZAT

\vfill
There are numerous methods for road sign recognition but the rubust and cost-effective solution is still an active research subject. The recognisability of traffic signs is affected by many variables, like luminous intensity, shading, partial coverage and other obstacles. The developed system is recognising road sings using machine learning techniques taking in consideration the above mentioned factors. The most important factor is accuracy and speed. The application displays the examined image and analyses it on background threads. The program extracts random rectangles from the original picture and decides if it contains a traffic sign or not, and if it does it categorises them.

This work is the result of my own activity. I have neither given nor received unauthorized assistance on this work.

\vfill

\end{abstractEN}


% ez a címoldal része
\maketitle
%% 

% a dolgozat tartalomjegyzéke -- ez automatikusan generálódik a STRUKTÚRA alapján.
{ \baselineskip 1ex
  \parskip 1ex
  \tableofcontents
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%         a dolgozat tartalma         %%%%%%%%%%%%



% a bevezető fejezet FILE-ja.
\include{intro}
\include{eddigieredmenyek}
\include{roadSigns}
\include{segmentation}
\include{preprocessing}
\include{neuralnet}
\include{output}
\include{egyszeruteszt}
\include{eredmenyek}
\include{tovabb}
\include{programs}

{
\bibliography{konyveszet}
\bibliographystyle{IEEEtranN}
\nocite{*}
}


\end{document}
